Comparative Evaluation of Spark and Flink Stream Processing

### 2017-03-05 paper/paper.tex
[paper] update stream setup section

\begin{flushleft}
\centering\LARGE {\bf Comparative Evaluation of Spark and Flink Stream Processing}

Supervisor: PD Dr. Michael Mock
\thispagestyle{empty}
\end{flushleft}
\newpage
\tableofcontents

@@

\section{Experiment Setup and Implementation}
This section describes the data stream setup, design of evaluation streaming workloads, and implementation details in Spark and Flink.

\subsection{Data Stream Setup}
Our streaming workloads read input data stream from Kafka. In order to simulate real-world uses cases we use datasets of Automatic Dependent Surveillance – Broadcast (ADS-B) messages that present the aircraft's position over time, comprise 22 fields of data such as aircraft ID, date message generated, longitude, latitude, and altitude.
\par In our experiment a data stream producer component reads the ADS-B datasets, then publish it to Kafka cluster to be consumed by the workloads in Spark and Flink. Figure 1 illustrates the data producer and the Kafka cluster setup.
The data stream is portioned into four portions over two server, while the data producer publish the stream records randomly to Kafka partitions.

@@

\begin{itemize}
\item Handling parallel input streams (e.g., Kafka Stream).
\item How to aggregate the state of input stream.
\item Manage the order of stream records.
\item How to provide and update global data model in stream processing task.
\item Evaluate the performance by measuring  the latency and throughput.
\end{itemize}
We present the description of workloads and the relation with these aspects, and th implementation details of Spark and Flink solutions in Section 3.2.1 \& 3.2.1. Afterward, In Section 4 we discuss the performance evaluation and analysis of workloads.

>>>>

\begin{flushleft}

 \thispagestyle{empty}
\centering\LARGE {\bf Comparative Evaluation of Spark and Flink Stream Processing}

\vspace{14pt}

\centering
 Lab: Data Science and Big Data MA-INF 4306,
 Winter Term 2016/2017, University of Bonn

\vspace{14pt}
\centering
 Ehab Qadah\\
 Supervisor: PD Dr. Michael Mock
\rule{\textwidth}{1pt}
\end{flushleft}
\newpage
\tableofcontents

@@

\section{Experiment Setup and Implementation}
This section describes the data stream setup, the design of evaluation streaming workloads, and the implementation details in Spark and Flink.

\subsection{Data Stream Setup}
The evaluation streaming workloads read an input data stream from Kafka, in order to simulate real-world use case we use datasets of Automatic Dependent Surveillance – Broadcast (ADS-B) messages that present the aircraft's position over time, comprise 22 fields of data such as aircraft ID, date message generated, longitude, latitude, and altitude etc.
\par In our experiment a data stream producer component reads the ADS-B message datasets, then publish them to Kafka cluster to be consumed by the workloads in Apache Spark and Apache Flink. Figure 4 illustrates the data producer and the Kafka cluster setup in all experiments.
The data stream is portioned into four portions over two server, while the data producer publish the stream records randomly to Kafka partitions, and all ADS-B messages are published to same topic, which is \texttt{datacorn}. Moreover, the data producer attach the streaming time at the ADS-B message line before publishing it to the Kafka topic, to be used in the latency calculation.

@@

\begin{itemize}
\item Handling parallel input streams (e.g., Kafka Stream).
\item How to aggregate the state of input stream.
\item Manage the order of stream records.
\item How to provide and update global data model in stream processing task.
\item Evaluate the performance by measuring  the latency and throughput.
\end{itemize}
We present the description of workloads and the relation with these aspects, also the implementation details of Spark and Flink solutions in Section 3.2.1 \& 3.2.1. Afterward, In Section 4 we discuss the performance evaluation and analysis of these workloads in both frameworks.
